---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  prompt = TRUE, 
  collapse = TRUE,
  comment = ""
)
library("ipsum")
```

# ipsum

[![Travis-CI Build Status](https://travis-ci.org/purrple/ipsum.svg?branch=master)](https://travis-ci.org/purrple/ipsum)

`ipsum` contains some functions to generate dummy text. This is inspired
from [bacon ipsum](https://baconipsum.com) so several examples used in the package 
and this file are meaty. To balance things, there are also examples using vegetables
and cran package names. 

## sentence

A sentence starts with a capital letter, contains several words, possibly with some commas and finishes with a dot. 

```{r}
sentence(meat)
```

## paragraph

A paragraph contains several sentences. 

```{r}
paragraph( vegs )
```

```{r}
paragraph( cran_package_names() )
```

## prose

Then we can put paragraphs together with `prose`

```{r}
prose(meat, n = 2)
```

# Printing

`sentence`, `paragraph` and `prose` return simple character vectors with S3 class `ipsum`. 
The package ships a `print` function that passes parameters to  [stringr::str_wrap](http://stringr.tidyverse.org/reference/str_wrap.html) for formatting : 

```{r}
recipee <- prose( c(meat, vegs), n = 5)
print( recipee, indent = 4, exdent = 2, width = 100 )
```
