---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
library("ipsum")
```

# ipsum

[![Travis-CI Build Status](https://travis-ci.org/purrple/ipsum.svg?branch=master)](https://travis-ci.org/purrple/ipsum)

`ipsum` contains some functions to generate dummy text. This is inspired
from [bacon ipsum](https://baconipsum.com) so several examples used in the package 
and this file are meaty. To balance things, there are also examples using vegetables
and cran package names. 

## sentence

A sentence starts with a capital letter, contains several words, possibly with some commas and finishes with a dot. 

```{r}
sentence(meat)
sentence(vegs)
```

## paragraph

A paragraph contains several sentences. 

```{r}
paragraph( meat )
paragraph( vegs )
paragraph( c(meat, vegs) )
paragraph( cran_package_names() )
```

## prose

Then we can put paragraphs together with `prose`

```{r}
prose(meat, n = 2)
prose(vegs, n = 2)
prose(cran_package_names(), n = 2)
```
